\documentclass{resume-classica}

\name{Nathanael Gentry}
\address{Greenville, South Carolina}
\mobile{(808) 859-0779}
\email{ngentry1@liberty.edu}
\linkedin{nathanael-gentry}

\begin{document}
\printheader
\begin{rSection}{Profile}
    I enjoy studying applied mathematics and computer science, and I aspire toward a career in data science. My robust academic record demonstrates my perseverance and self-motivation.
\end{rSection}

\begin{rSection}{Education}
    \begin{rSubsectionList}{Liberty University}{2017 - 2021}{Bachelor of Science, Mathematics (Honors)}{GPA: 4.00}
        \begin{rLabeledList}{\scshape}
            \item{Minors}{Computer Science and Philosophy}{1}
            \item{Skills}{Lisp, Python, C++, Mathematica, Bash, VBA, \LaTeX{}}{1}
            \item{Courses}{Algorithms and Data Structures, Introductory Statistical Analysis, Calculus III;\newline Discrete Mathematics, Linear Algebra, Elementary Number Theory}{2}
            \item{Self-Study}{Database System Concepts, Introduction to Artificial Intelligence (MIT OCW 6.034)}{1}
            \item{Honors}{Kappa Mu Epsilon Mathematics Honor Society\vspace{2mm}}{1}
        \end{rLabeledList}
    \end{rSubsectionList}
\end{rSection}

\begin{rSection}{Projects and Interests}
    \begin{rSubsectionList}{``Exploring PageRank''}{Spring 2019}{}{}
        A twenty-page synthesis of the basic eigentheory underlying Google's Web page ranking algorithm, written as an honors project in linear algebra. To be published in \textit{The Kabod}, Liberty University's student honors journal.
    \end{rSubsectionList}

    \begin{rSubsectionParagraph}{AuDiTeX}{Summer 2019}{}{}
        An idea, still in early development, to revise T.V. Raman's robust math-to-speech system AsTeR for modern speech synthesizers. To provide a standard way for visually impaired students to access mathematics, this project aims toward a plugin to produce audio renderings of \LaTeX{} documents within the standard compilation process.
    \end{rSubsectionParagraph}
\end{rSection}

\begin{rSection}{Professional Experience}
    \begin{rSubsectionList}{COMPACFLT}{Summer 2018}{DoD Pathways Intern (GS-04)}{Pearl Harbor, HI}
        \item Learned Python and shell scripting by implementing Docker service containerization for naval network software development; gained familiarity with Ruby
        \item Optimized development environment and documentation for new network developers
        \item Streamlined asset delivery and media inventory for technical refresh of 1,000+ workstations
    \end{rSubsectionList}

    \begin{rSubsectionList}{Liberty University Motorsports}{Spring 2019}{Formula SAE Simulation-Analysis Developer}{Lynchburg, VA}
        \item Built an Excel VBA application to calculate Formula SAE Electric competition scores from racing vehicle simulations produced in OptimumLap.
        \item Implemented functions to convert the internal-combustion engine simulations of OptimumLap to electric motor equivalents.
        \item Designed a database system to compare racing vehicle simulations and pinpoint significant design changes.
    \end{rSubsectionList}
    
    \begin{rSubsectionList}{Starn O'Toole Marcus \& Fisher}{Summer 2017}{Office Intern}{Honolulu, HI}
        \item Managed digitizing and condensing 350+ case file archives.
        \item Saved employer \$2500+ in storage fees each year through on-site storage optimization.
        \item Assisted paralegals with research for three clients, including a large hotel chain.
    \end{rSubsectionList}
\end{rSection}

\begin{rSection}{Activities}
    \begin{rLabeledList}{\bfseries}
        \item{Choral Ensembles}{Timberlake Baptist Chorale, Liberty Univeristy Concert Choir}{1}
        \item{Elective Piano}{Liberty University Piano Showcase, Library Pianist}{1}
    \end{rLabeledList}
\end{rSection}

\end{document}