% -*- TeX-engine: xetex; -*-

\documentclass{awesome-cv}
\geometry{left=1.0cm, top=1.3cm, right=1.0cm, bottom=1.0cm, footskip=0cm}

% -------------------------------------------------------------------------------
% AwesomeCV Configuration
% -------------------------------------------------------------------------------
%
% 1. Fonts.
% Get the plan Latin Modern look back.
\newcommand*{\lmr}{\fontfamily{lmr}\selectfont}
\fontdir{}

\renewcommand*{\footerfont}{\lmr}
\renewcommand*{\bodyfont}{\lmr}

% 2. Configuration styles.
% Global font sizes
\newcommand{\namefontsize}{\fontsize{24pt}{1em}}
\newcommand{\bodyfontsize}{\fontsize{10.5pt}{1em}}

% Fundamental structures.
\renewcommand*{\headerfirstnamestyle}[1]{{\namefontsize\bodyfont\color{text} #1}}
\renewcommand*{\headerlastnamestyle}[1]{\namefontsize\bodyfont\color{text}{#1}}
\renewcommand*{\headerpositionstyle}[1]{{\fontsize{11pt}{1em}\bodyfont\scshape\color{text}#1}}
\renewcommand*{\headersocialstyle}[1]{{\fontsize{12pt}{1em}\bodyfont\itshape\color{text} #1}}
\renewcommand*{\headerquotestyle}[1]{{\fontsize{11pt}{1em}\bodyfont\color{text} #1}}
\renewcommand*{\sectionstyle}[1]{{\fontsize{14pt}{1em}\bodyfont\bfseries\scshape\color{text} #1}}
\renewcommand*{\subsectionstyle}[1]{{\bodyfontsize\bodyfont\scshape\textcolor{text}{#1}}}
\renewcommand*{\paragraphstyle}{\bodyfontsize\bodyfont\upshape\color{text}}

% For elements of entry.
\renewcommand*{\entrytitlestyle}[1]{{\bodyfontsize\bodyfont\bfseries\color{darktext} #1}}
\renewcommand*{\entrypositionstyle}[1]{{\bodyfontsize\bodyfont\scshape\color{graytext} #1}}
\renewcommand*{\entrydatestyle}[1]{{\bodyfontsize\bodyfont\slshape\color{graytext} #1}}
\renewcommand*{\entrylocationstyle}[1]{{\bodyfontsize\bodyfont\slshape\color{text} #1}}
\renewcommand*{\descriptionstyle}[1]{{\bodyfontsize\bodyfont\upshape\color{text} #1}}

% 3. Custom spacings.
% Header.
\renewcommand*{\acvHeaderAfterNameSkip}{3mm}
\renewcommand*{\acvHeaderIconSep}{\hskip0.3em\relax}
\renewcommand*{\acvHeaderSocialSep}{\hskip0.5em\relax$\diamond$\hskip0.5em\relax}

% Sections.
\renewcommand*{\acvSectionTopSkip}{5pt}
\renewcommand*{\acvSectionContentTopSkip}{5pt}

% Others.
\renewcommand{\acvItemsBetweenParSkip}{5pt}
\renewcommand{\acvItemsBeforeStartSkip}{2pt}
\renewcommand{\acvCvAfterEntrySkip}{5pt}

% 4. Colors
\definecolor{awesome}{HTML}{000000}
\setbool{acvSectionColorHighlight}{false}

% 5. Pictures
% GitHub icon override.
\renewcommand*{\faGithubSquare}{\faGithub}

% -------------------------------------------------------------------------------

%\photo[circle]{npjg-2018.jpg}{1cm}
\name{Nathanael}{Gentry}

\mobile{(808) 859-0779}
\github{npjg}
\email{ngentry1@liberty.edu}
% \linkedin{nathanael-gentry}
% \quote{Seeking an analytics internship or research experience for summer 2020.}

\usepackage[super]{nth}

\begin{document}
\makecvheader[C]

%\makecvfooter
%  {\today}
%  {Nathanael Gentry~~~·~~~Resume}
%  {\thepage}

% Education
\cvsection{Education}

\begin{cventries}
  \cventry
  {Liberty University}
  {Bachelor of Science, Mathematics}
  {\entrydatestyle{2017 -- 2021}}
  {\textbf{GPA: 4.00}}
  {
    \begin{cvlabeleditems}
    \item{Minors}{Computer Science and Piano Performance}
    \item[2]{Skills}{C++, Python, Emacs Lisp, R, JavaScript, Ajax, Lilypond,
        XPath, jQuery, HTML/CSS, Mathematica, Sage, \TeX{}, Bash, VBA}
    \item{Societies}{Honors Program, Concert Choir, Formula SAE}
    \end{cvlabeleditems}
  }
\end{cventries}


% Papers
\cvsection{Papers}

\begin{cventries}
  % Need to add more logic to eliminate bad spaces
  \cventry
  {Exploring PageRank}
  {}
  {\entrydatestyle{Spring 2019}}
  {}
  {
    A synthesis of the eigentheory underlying Google's ranking method, written as an honors project in linear algebra.
  }

  %\cventry
  %{Warranted Christian Belief and the Inadequacy Thesis}
  %{}
  %{\entrydatestyle{Spring 2020}}
  %{}
  %{Presented at the first annual Liberty University Undergraduate Philosophy Conference}

  \cventry
  {Active-Adaptive Control for Dielectric Elastomer-Based Robotics: A Review}
  {}
  {\entrydatestyle{Fall 2020}}
  {}
  {A literature review paper from the Liberty University Mechatronics Research Lab.}
\end{cventries}


% Experience
\cvsection{Experience}

\begin{cventries}
  \cventry
  {Google Summer of Code (ScummVM)}
  {Software Engineer Intern}
  {}
  {Summer 2020 -- Present}
  {
    \begin{cvitems}
      \item Currently collaborating on a reimplementation of Macromedia Director, targeting hundreds of content titles.
      \item Gained experience with C++ graphics programming in a complete redesign of the engine's rendering pipeline.
      \item Introduced to reverse-engineering with Ghidra and custom software tools.
    \end{cvitems}
  }

  \cventry
  {Departments of Mathematics and Engineering}
  {Student Researcher}
  {}
  {Spring 2019 -- Present}
  {
    \begin{cvitems}
    \item Currently working with the Mechatronics Research Lab (Dr. Hector Medina) to implement Python machine-learning control for using dielectric elastomers to stabilize laser communication systems.
    \item Refined a Web interface and implemented a backend for \TeX{} Math Here, a browser extension that brings mathematical typesetting to popular Web interfaces. \textit{(2020 Research Week \nth{1} Place Undergraduate Applied Oral Presentation)}
    \item Built an Excel VBA application and database framework to calculate Formula SAE Electric competition scores from racing vehicle simulations produced in OptimumLap.
    \end{cvitems}
  }

  \cventry
  {Self-Employed}
  {Freelance Developer}
  {}
  {Summer 2019}
  {
    \begin{cvitems}
    \item Started several open-source projects, including Emacs extensions and a \TeX{} package.
    \item Volunteered 25+ hours at a large food bank for database migration and
     documentation updates.
    \end{cvitems}
  }

  \cventry
  {COMPACFLT (Pearl Harbor)}
  {Department of the Navy Pathways Intern (GS-04)}
  {}
  {Summer 2018}
  {
    \begin{cvitems}
    \item Learned Python and shell scripting by implementing Docker service containerization for naval network software development; gained familiarity with Ruby.
    \item Optimized development environment and documentation for new network
      developers.
    \item Streamlined asset delivery and media inventory for technical refresh of
      1,000+ workstations.
    \end{cvitems}
  }
\end{cventries}

% Rewards.
\cvsection{Awards}
  \vspace{14pt}
  \descriptionstyle{
    \begin{cvlabeleditems}
    \item{Wooldridge Award}{2020. Awarded to one rising senior math major for academic achievement and service.}
    \item{Research Week}{2020. Undergrad Research Week, for \TeX{} Math Here browser extension project.}
    \item{Piano Showcase}{2018, 2019. Competitively-placed classical performance in the grand concert hall.}
    \end{cvlabeleditems}}
\end{document}
